\input{preamble}

\mytitle{Curriculum Vitae}
\definecolor{color1}{rgb}{0.0, 0.45, 0.81}
\definecolor{mark_color}{rgb}{0, 0, 0}

\begin{document}
\pagestyle{headonly}

\makecvtitle

\cvitem{}{\emph{\vspace{-1cm}\\
$\quad$ Ph.D student in Physics and Astronomy, focusing on gravitational wave analysis and machine learning applications.}}

\section{Contact}

\cvitem{Email}{\href{mailto:c.anselmo@campus.unimib.it}{c.anselmo@campus.unimib.it}}
\cvitem{Address}{Universit\`{a} degli Studi di Milano-Bicocca, Piazza della Scienza 3, 20126 Milano, Italy.}
%\cvitem{Website}{\href{}{}}

%\cvitem{Citizenship}{Italy, EU.}

%\section{Academic positions}

%\section{Past academic positions}

\section{Education}

\cventry{2024 - current}{Ph.D, Physics and Astronomy}{Universit\`{a} degli Studi di Milano-Bicocca}{Milan, Italy}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Supervisor}}: D. Gerosa.
\end{tabular}

\vspace{0.2cm}
\cventry{2022-2024}{Master's degree in Astronomy and Astrophysics}{\newline Universit\`{a} La Sapienza}{Rome, Italy}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Final degree grade}}: 110/110 with distinction (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Average class grade}}: 29.46/30 with XXX distinctions (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Thesis advisors}}: P. Pani, A. Maselli.\\

\end{tabular}

\vspace{0.2cm}
\cventry{2019-2022}{Bachelor's degree in Physics}{Universit\`{a} degli Studi Federico II}{Naples, Italy}{}{}
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Final degree grade}}: 110/110 with distinction (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Average class grade}}: XXX/30 with XXX distinctions (``cum laude'').\\
&\hspace{0.4cm} &$\circ\;\;${\textit{Thesis advisor}}:  S. Capozziello.\\
\end{tabular}


\vspace{0.2cm}
\cventry{2014-2019}{Scientific High School degree}{\newline Liceo Scientifico Torricelli}{Naples, Italy}{}{}  %
\vspace{-0.1cm}
\begin{tabular}{rcl}
&\hspace{0.4cm} &$\circ\;\;${\textit{Final grade}}:  100/100.\\
\end{tabular}


\section{Metrics}

%\input{metricspapers.tex}

%\textbf{Full list of publications} available 
%mark_CVshort
%below and
%mark_CVshort
%at \href{}{}}.

%\vspace{0.2cm}

\input{metricstalks.tex}

%\textbf{Full list of presentations} available
%mark_CVshort
%below and
%mark_CVshort
%at \href{}{\texttt{}}.


\section{Awards}

\textbf{\textcolor{black}{Career prizes:}}
\vspace{0.1cm}

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ 
PRD Reviewer Excellence Award, American Physical Society.}{2025}
\vspace{-0.1cm}


\vspace{0.2cm}


\section{Teaching}

%\vspace{0.1cm}
\textbf{\textcolor{black}{Taught classes:}}
\vspace{0.1cm}
\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Machine learning applied to physical systems.}}{2024-current} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Artificial Intelligence BSc, Pavia+Milano+Milano-Bicocca joint degree.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ 
\href{https://dgerosa.github.io/machinelearning4physics}{\texttt{dgerosa.github.io/machinelearning4physics}}}{} 
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Scientific computing with python}.
% (113R-06).
}{2023-current} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Physics PhD, Milano-Bicocca.}{} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$
\href{https://dgerosa.github.io/scientificcomputing}{\texttt{dgerosa.github.io/scientificcomputing}}}{} 
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Astrostatistics and machine learning}.% (F5802Q014/20).
}{2022-current} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Astrophysics and Space Science MSc, Milano-Bicocca.}{} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$
\href{https://dgerosa.github.io/astrostatistics}{\texttt{dgerosa.github.io/astrostatistics}}}{} 

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Classical physics.} %(E3101Q130).
}{2021-2023} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Computer Science BSc, Milano-Bicocca.}{} 

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Year 1 Astrolab}.}{2020-2021} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Physics BSc, Birmingham.}{} 


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Year 1 student tutoring}.}{2019-2021} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Physics BSc, Birmingham.}{} 


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Black holes and gravitational waves}.}{2019-2020} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Midlands Physics Alliance Graduate School (MPAGS) PhD, Birmingham.}{} 


\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Part III General relativity}  (teaching assistant).}{2015-2016} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Mathematics MSc, Cambridge.}{} 

\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ \textit{Part II General relativity}  (teaching assistant).}{2014-2016} \vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Natural Sciences BSc, Cambridge.}{} 




\section{Service}




\textbf{\textcolor{black}{Journal referee}}\vspace{0.1cm}\\
\begin{tabular}{@{\hskip 0.4cm}l@{\hskip 0.4in}l}
$\circ\;$ Nature Astronomy,  & $\circ\;$   Reports on Progress in Physics,  \\
$\circ\;$ Nature Communications,  & $\circ\;$   European Physical Journal Plus,   \\
$\circ\;$ Science, & $\circ\;$ European Physical Journal C,  \\
$\circ\;$ Science Advances, & $\circ\;$  Europhysics Letters, \\
$\circ\;$ Physical Review Letters, & $\circ\;$  Physics Letters A, \\
$\circ\;$ Physical Review D,  & $\circ\;$   Scientific Reports, \\
$\circ\;$  The Astrophysical Journal Letters,  &  $\circ\;$ Annals of Physics \\
$\circ\;$ The Astrophysical Journal,  &  $\circ\;$ Astrophysics and Space Science, \\
$\circ\;$  Monthly Notices of the Royal Astronomical Society, & $\circ\;$ Journal of Open Source Software,  \\
$\circ\;$  Classical and Quantum Gravity, & $\circ\;$ SoftwareX, \\
$\circ\;$  Astronomy \& Astrophysics & $\circ\;$Taylor and Francis Press (textbooks).  \\
$\circ\;$  General Relativity and Gravitation, & %$\circ\;$  \\
\end{tabular}

\vspace{0.2cm}

I refereed papers written by the LIGO/Virgo/KAGRA Collaboration, the NanoGRAV Collaboration, and the SXS Collaboration.


\vspace{0.2cm}



% Also Universe, Galaxies, Symmetry

 \textbf{\textcolor{black}{Journal editor}}\vspace{0.1cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Classical and Quantum Gravity, Focus Issue \textit{``Numerical Relativity Beyond General Relativity".}}{2019} \vspace{-0.1cm}
\vspace{0.2cm}


 \textbf{\textcolor{black}{Grant proposal reviewer}}. Panel memberships marked with *.\vspace{0.1cm}\\
 %
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ ERC, Starting Grants, European Union;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ ERC, Advanced Grants, European Union;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ COST Actions, European Union;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ ESA, Voyage 2050 Topical Teams, Europe;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NASA, Astrophysics Theory Program (ATP), USA;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NASA, Postdoctoral Program (NPP), USA;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NASA, Graduate Fellowship Program (NESSF/FINESST), USA;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NSF, CAREER program, USA;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NSF, Physics Division Grants, USA;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NSF, Astronomy Division Grants, USA;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, Gravitational Waves Consolidated Grant Panel, UK;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, Astronomy Consolidated Grant Panel, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, Rutherford Fellowships, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ EPSRC, Hawking Fellowships, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Royal Society, University Research Fellowships, UK;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ STFC, DiRAC HPC cluster, UK;*}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ MUR, Montalcini Fellowships, Italy;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ MUR, Valutazione della Qualità della Ricerca (VQR), Italy;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Cariplo Foundation, Italy;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Humboldt Research Fellowships, Germany;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Dim Origines Grants, France;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ NWO, Veni Fellowships, The Netherlands;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Swiss NSF, Ambizione Fellowships, Switzerland;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Irish Research Council, Laureate Programme, Ireland;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Fonds de la Recherche Scientifique, Grants and Fellowship Call, Belgium;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ National Science Centre, Poland;}{}
\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Research Grants Council, Hong Kong.}{}
\vspace{-0.1cm}
 
%\begin{tabular}{@{\hskip 0.4cm}l}
%$\circ\;$ \\
%$\circ\;$ ERC, Advanced Grants, Europe;\\
%$\circ\;$ ESA, Voyage 2050 Topical Teams, Europe;* \\
%$\circ\;$ NASA, Astrophysics Theory Program (ATP), USA;* \\
%$\circ\;$ NASA, Postdoctoral Program (NPP), USA;\\
%$\circ\;$ NASA, Graduate Fellowship Program (NESSF/FINESST), USA; \\
%$\circ\;$ NSF, CAREER program, USA;\\
%$\circ\;$ NSF, Physics Division Grants, USA;\\
%$\circ\;$ STFC, Astronomy Grant Panel (AGP Consolidated), UK;\\
%$\circ\;$ STFC, Rutherford Fellowships, UK;\\
%$\circ\;$ Royal Society, University Research Fellowships, UK;\\
%$\circ\;$ STFC, DiRAC HPC cluster, UK;*\\
%$\circ\;$ Irish Research Council, Laureate Programme, Ireland;\\
%$\circ\;$ Fonds de la Recherche Scientifique, Grants and Fellowship Call, Belgium;\\
%$\circ\;$ Research Grants Council, Hong Kong.
%\end{tabular}


\vspace{0.2cm}
%\newpage{}
\textbf{\textcolor{black}{Hiring board member}} for University of Birmingham (UK), University of Milano-Bicocca (Italy), Sapienza University \\ \phantom{xx} of Rome (Italy), University of Padua (Italy). 
%\vspace{-0.1cm}

\vspace{0.2cm}
\textbf{\textcolor{black}{PhD thesis examiner}} for SISSA (International School for Advanced Studies; Italy), Imperial College London (UK),
 \\ \phantom{xx} Monash University (Australia),  Cardiff University (UK), 
 University of Pisa (Italy), University of Milan (Italy). %\vspace{-0.1cm}


\vspace{0.2cm}
\textbf{\textcolor{black}{Organized conferences}}\vspace{0.05cm}\\
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ GWfreeride: carving the AI gradient in gravitational-wave astronomy}{2026}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Sexten Center for Astrophysics, Italy. \href{https://sites.google.com/unimib.it/gwfreeride}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ XXVI SIGRAV conference on general relativity and gravitation}{2025}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Milano-Bicocca, Italy. \href{https://sites.google.com/unimib.it/sigrav2025}{\texttt{[link]}}
}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Theoretical Horizons in Unraveling Relativity, Astrophysics, and Mergers (THURAM).
}{2024}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Gran Sasso Science Institute, Italy. \href{https://davidegerosa.com/thuram/}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Gravitational-wave snowballs, populations, and models}{2025}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Sexten Center for Astrophysics, Italy. \href{https://sites.google.com/unimib.it/gwsnowballs}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Challenges and future perspectives in gravitational-wave astronomy: O4 and beyond}{2024}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$  Lorentz Center, Leiden, the Netherlands. \href{https://www.lorentzcenter.nl/challenges-and-future-perspectives-in-gravitational-wave-astronomy-o4-and-beyond.html}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Linking Advances in our Understanding of Theoretical Astrophysics and Relativity to Observations}{2024}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$  (LAUTARO). University of Milano-Bicocca, Italy. \href{https://davidegerosa.com/lautaro/}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Big data within science and industry.}{2023}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Milano-Bicocca, Italy. \href{https://sites.google.com/unimib.it/bigdatamasterclass}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Gravitational-wave populations: what's next?}{2023}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Milano-Bicocca, Italy. \href{https://sites.google.com/unimib.it/gwpopnext}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Gravitational-wave Excellence Alliance Training (GrEAT) PhD school.}{2019}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Birmingham, UK. \href{https://sites.google.com/view/greatnetworkschool}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Numerical Relativity beyond General Relativity.}{2018}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Benasque Science Center, Benasque, Spain. \href{https://www.benasque.org/2018relativity}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ APS 34$^\textsf{th}$ Pacific Coast Gravity Meeting.}{2018}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Caltech, USA. \href{http://www.tapir.caltech.edu/~pcgm34}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ The migration issue: from protoplanets to supermassive black holes.}{2017}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ University of Cambridge, UK. \href{https://www.kicc.cam.ac.uk/events/copy_of_past-events/the-migration-issue-from-protoplanets-to-supermassive-black-holes-1/the-migration-issue-from-protoplanets-to-supermassive-black-holes}{\texttt{[link]}}}{} \vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Einstein's Legacy: Celebrating 100 $\!$yrs of General Relativity.}{2015}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\phantom{\circ}\;$ Queen Mary University of London, UK.}{} \vspace{-0.1cm}


%\newpage{}

%

%\textbf{\textcolor{black}{Outreach activities}}\vspace{0.05cm}\\
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ TV Interview on gravitational waves and black-hole kicks aired on Cambridge TV.}{2016}\vspace{-0.1cm}
%\cvitem{}{\hspace{0.8cm}(see \href{http://www.cambridge-tv.co.uk/davide-gerosa-black-holes/)}{\textit{cambridge-tv.co.uk/davide-gerosa-black-holes}}).\vspace{-0.1cm}}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Actively involved in the Cambridge Science Festival, faculty of Mathematics.}{2015}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Research coverage by the Caltech outreach journal: CURJ, Vol.15 No.1 (2014).}{2014}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Scientific journalist for the Italian on-line newspaper \href{http://www.ilsussidiario.net}{\textit{ilsussidiario.net}.}}{since 2013}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Astronomy and relativity lectures to high-school students.}{since 2011}\vspace{-0.1cm}

%



%\newpage
\vspace{0.2cm}
\textbf{\textcolor{black}{Professional recognition and service}}\vspace{0.05cm}
\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Local coordinator, TEONGRAV initiative, National Institute for Nuclear Physics (INFN).}{2025 - current}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Erasmus program coordinator, Physics department, University of Milano-Bicocca.}{2024 - current}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  European Consortium for Astroparticle Theory (EuCAPT), council member.}{2022 - current}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Full Professorship in Astrophysics (ASN 02/C1).}{2022}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Full Professorship in Theoretical Physics (ASN 02/A2).}{2022}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Associate Professorship in Astrophysics (ASN 02/C1).}{2020}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Italian Habilitation  to Associate Professorship in Theoretical Physics (ASN 02/A2).}{2018}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Seminar organizer, AstroBicocca seminar series, Milano-Bicocca.}{2021-2024}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Academic advisory team for the BlueBEAR HPC cluster, Birmingham.}{2019-2021}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Seminar organizer, TAPIR seminar series, Caltech.}{2018-2019}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Caltech representative, committee of the European COST Action ``GWverse''.}{2017-2019}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  PhD student representative, Gravitational Physics committee, UK Institute of Physics.}{2014-2016}\vspace{-0.1cm}
%
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$  Undergraduate student representative, Physics Department, University of Milan.}{2008-2012}\vspace{-0.1cm}


%$\circ\;$ GWIC 3G Science case subcommittee, & $\circ\;$ Royal Astronomical Society,\\

\vspace{0.2cm}
\textbf{\textcolor{black}{Memberships}}\vspace{0.05cm}\\
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ International Society on General Relativity and Gravitation (ISGRG), life member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Italian Society of General Relativity and Gravitational Physics (SIGRAV), honorary life member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ International Astronomical Union (IAU), Individual member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ American Physical Society (APS), member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Italian Physical Society (SIF), member.}{}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ European Astronomical Society (EAS), member.}{}\vspace{-0.1cm}
%\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Association of ERC Grantees (AERG), member.}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ Italian Center for Supercomputing (ICSC).}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ TEONGRAV national initiative (Gravity Theory), National Institute for Nuclear Physics (INFN).}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ AI\_INFN National Initiative (Artificial Intelligence), National Institute for Nuclear Physics (INFN).}{}\vspace{-0.1cm}
\cvitemwithcomment{}{\hspace{0.4cm}$\circ\;$ LISA Consortium, community member.}{}\vspace{-0.1cm}

\vspace{-0.32cm}

\section{Skills}
\cvitem{Programming languages}{Python (advanced), Bash, Mathematica, C. 
}
\cvitem{Other scientific tools}{TensorFlow, LIGO lalsuite, LaTex, git, slurm, cloud computing, website development.}
\cvitem{Languages}{English (fluent), Italian (native).}

\vspace{-0.32cm}
\section{Hobbies}
Anime enthusiast \textbullet\ Avid reader of psychology and behavioural science books, as well as novels \textbullet\ Cooking and experimenting in the kitchen \textbullet\ Alternative and indie rock with Japanese influences \textbullet\ Long walks \textbullet\ Active lifestyle

%mark_CVshort

\pagebreak
\section{Full publication list}\vspace{0.2cm} 

\input{parsepapers.tex}

\pagebreak
\section{Full presentation list}\vspace{0.2cm} 

\input{parsetalks.tex}
%mark_CVshort

\end{document}
